Automated topic naming to support cross-project analysis of software maintenance activities

### 2011-01-21 msr/msr2011.tex
minor fixes, removed commented intro for clarity, fixing wording

@@

\noindent \textbf{Analysis of the unsupervised labelling} -- %Based on the labels, and our manual topic labelling, 
%we compared the results of the unsupervised word matching approach. 
For each quality we assessed whether unsupervised labels matched the manual annotations. To be clear, the manual annotations were not used to train the labeling process.
Figure \ref{fig:maxdb-unsup-results} shows our results for MaxDB and MySQL. 
\todo[inline]{NEIL: this section should be updated to explain F-measure}
Our performance is measured using the Receiver Operating Characteristic area-under-curve value~\cite{Fawcett2006861}, abbreviated \emph{ROC}. 
ROC values provide a score, similar to school letter-grades (A is 0.9, C is 0.6), reflecting how well a particular learner performed for the given data. 
ROC maps to the more familiar concepts of precision/sensitivity and recall/specificity: it plots the true positive rate (sensitivity) versus the false positive rate (1 - specificity). 
A perfect learner has a ROC value of 1.0, reflecting perfect recall and precision. 
A ROC result of 0.5 would be equivalent to a random learner (that is, issuing as many false positives as true positives). 
The %area under the -- NE confusing to have area again ... and not importantana
ROC of a classifier is equivalent to the probability that the classifier will rank a randomly chosen positive instance higher than a randomly chosen negative instance.

@@

% para 2 we did this to validate and show we did it
% Experiment description -- origin of wordbags
% NEIL - shortening this 
We validated our topic labelling techniques using multiple experiments. 
We first conducted unsupervised labelling using word-lists. 
Our next approach was supervised, using single-label and multi-label learners. 
% Using unsupervised word-list analysis we set up two NFR topic labelling experiments: 
% our \textsf{exp2} experiment used small but accurate word-lists, while \textsf{exp3} used large general word-lists derived from WordNet.
% The performance of these techniques differed per NFR but both \textsf{exp2} and \textsf{exp3} had similar performance.
%Our \textsf{exp2} experiment used small accurate word bags to label topics but performed just as well as \textsf{exp3}, which used many more general terms from WordNet.
% we could can improve auto labelling with ML
% Our third experiment showed that with some supervision, and by using efficient machine learners based on Naive Bayesian classifiers, we could improve the accuracy of automatic topic labelling even further.
% Our fourth experiment evaluated the effectiveness of multi-label learners, such as HOMER. 
Both kinds of learners performed well with area under the ROC curve values between $0.6$ and $0.8$.

>>>>

Changes to software systems, revisions, do not occur without
reason. 
The reason or purpose is often related to requirements 
Often one revision might have multiple purposes ranging from
maintenance issues, quality issues, requirements, features or a
response to a bug report.
These purposes often are exhibited as latent topics that relate to
many development artifacts such as:
 version control revisions, bug reports, and mailing-list discussions.

@@

\noindent \textbf{Analysis of the unsupervised labelling} -- %Based on the labels, and our manual topic labelling, 
%we compared the results of the unsupervised word matching approach. 
For each quality we assessed whether unsupervised labels matched the manual annotations. To be clear, the manual annotations were not used to train the labeling process.
Figure \ref{fig:maxdb-unsup-results} shows our results for MaxDB and MySQL. 
\todo[inline]{NEIL: this section should be updated to explain F-measure}
Our performance is measured using the Receiver Operating
Characteristic area-under-curve value~\cite{Fawcett2006861},
abbreviated \emph{ROC}, and the F-measure. 
ROC values provide a score, similar to school letter-grades (A is 0.9, C is 0.6), reflecting how well a particular learner performed for the given data. 
ROC maps to the more familiar concepts of precision/sensitivity and recall/specificity: it plots the true positive rate (sensitivity) versus the false positive rate (1 - specificity). 
A perfect learner has a ROC value of 1.0, reflecting perfect recall and precision. 
A ROC result of 0.5 would be equivalent to a random learner (that is, issuing as many false positives as true positives).

The %area under the -- NE confusing to have area again ... and not importantana
ROC of a classifier is equivalent to the probability that the classifier will rank a randomly chosen positive instance higher than a randomly chosen negative instance.
F-measure is the harmonic mean of precision and recall.

@@

% para 2 we did this to validate and show we did it
% Experiment description -- origin of wordbags
% NEIL - shortening this 
We validated our topic labelling techniques using multiple experiments. 
We first conducted unsupervised labelling using word-lists. 
Our next approach was supervised, using single-label and multi-label learners. 
% Using unsupervised word-list analysis we set up two NFR topic labelling experiments: 
% our \textsf{exp2} experiment used small but accurate word-lists, while \textsf{exp3} used large general word-lists derived from WordNet.
% The performance of these techniques differed per NFR but both \textsf{exp2} and \textsf{exp3} had similar performance.
%Our \textsf{exp2} experiment used small accurate word bags to label topics but performed just as well as \textsf{exp3}, which used many more general terms from WordNet.
% we could can improve auto labelling with ML
% Our third experiment showed that with some supervision, and by using efficient machine learners based on Naive Bayesian classifiers, we could improve the accuracy of automatic topic labelling even further.
% Our fourth experiment evaluated the effectiveness of multi-label learners, such as HOMER. 
Both kinds of learners performed well with 
%area under the 
ROC values between $0.6$ and $0.8$.
